\myTitle

### 2015-04-03 tex/main-body-text.tex
Final things to prep for final submission.

Plateaus were only observed for the data set 
with the highest pairwise $F_{ST}$ value $(0.03)$. Plateau records were similar, although 
the length of each plateau record was slightly longer for {\sc flockture} and on average had more runs converging on
the largest plateau. Multiple runs of {\sc flockture} demonstrated that the differences are well within the
variability that we would expect from randomizing the initial grouping of individuals to 
initiate the algorithms.

@@

The number and length of plateaus {\sc flockture} encountered quickly 
diminished as the amount of differentiation among populations decreased. For the microsatellite data sets,
when $F_{ST}$ was less than 0.0337, no plateau record
contained a plateau of length six or greater. No plateaus were observed 
(i.e. no two runs of {\sc flockture} gave exactly the same solution) when 
$F_{ST}$ was smaller than 0.02187. Results from the SNP data sets
were concordant.
Only simulated data sets with pairwise $F_{ST}$ values greater 0.0323 had plateau records with a 
plateau greater than six. Despite the lack of plateaus observed for many of the simulated data sets, 
graphs of the normalized likelihood values from the {\sc flockture} run with the highest 
likelihood were indicative of population structure (Fig~\ref{fig:FvSdistruct}).

>>>>

Plateaus were only observed for the data set 
with the highest pairwise $F_{ST}$ value $(0.03)$. Plateau records were similar, although %ref supplementary table FLOCKvFLOCKTURE_PlateauTable.pdf
the length of each plateau record was slightly longer for {\sc flockture} and on average had more runs converging on
the largest plateau (see Supporting Information). Multiple runs of {\sc flockture} demonstrated that the differences are well within the
variability that we would expect from randomizing the initial grouping of individuals to 
initiate the algorithms.

@@

The number and length of plateaus {\sc flockture} encountered quickly %ref supp tables FLOCKTURE_PlateauTable_XX.pdf
diminished as the amount of differentiation among populations decreased (Supporting Information). For the microsatellite data sets,
when $F_{ST}$ was less than 0.0337, no plateau record
contained a plateau of length six or greater. No plateaus were observed 
(i.e. no two runs of {\sc flockture} gave exactly the same solution) when 
$F_{ST}$ was smaller than 0.02187. Results from the SNP data sets
were concordant.
Only simulated data sets with pairwise $F_{ST}$ values greater 0.0323 had plateau records with a 
plateau greater than six. Despite the lack of plateaus observed for many of the simulated data sets, 
graphs of the normalized likelihood values from the {\sc flockture} run with the highest 
likelihood were indicative of population structure (Fig~\ref{fig:FvSdistruct}).
